Competing Bandits

### 2018-08-04 paper/competing_bandits.tex
updates to paper

We now re-run the same simulations but let $X = 200$ so that firm 2 has an ``incumbency" advantage. Recall that $X$ controls the number of rounds the firm is in the market by itself before the other firm enters and so in these rounds agents arrive and must choose firm 2. After $X$ rounds, firm 1 enters the market and each agent that enters in subsequent periods must select between the two firms.

@@

Table \ref{ht_incum} shows the results of the simulations for the Heavy Tail prior. $TS$ is a dominant strategy for the incumbent when $X$ is sufficiently high. In the appendix we include additional simulations where $X = 50$ and observe that $TS$ is not always a dominant strategy in this case. These results are robust across the different priors we considered as well as across agent response models. Namely, for sufficiently large $X$, $TS$ is a dominant strategy for the incumbent.

Whereas with simultaneous entry $TS$ was a worse strategy than $DG$ (for small warm start), by allowing one firm to have a first mover advantage and be a monopolist in the market in the early rounds we incentivize the monopolist to play the ``best" algorithm. The intuition for this is that competition forces the firms to worry about their reputation which dissuades them from committing to algorithms that involve pure exploration. In some sense one can view allowing one firm to temporarily be a monopolist as temporarily relaxing the ``incentive" component of exploration, exploitation, and incentives so that the incumbent firm only faces the classic tradeoff between exploration and exploitation. The incumbent only needs to worry about her reputation after $X$ periods when the entrant comes into the market and again needs to worry about incentivizing agents to select them over their competition. As a result, the incumbent is incentivized to commit to an algorithm that does exploration in the early rounds since she no longer suffers the same reputational cost that she would suffer under competition as long as the $X$ is sufficiently large that she can begin to recover the reputational costs of exploration.

>>>>

We now fix the same parameters as before, fixing a warm start of $k = 20$ [we should re-run this] but let $X = 200$ so that firm 2 has an ``incumbency" advantage. Recall that $X$ controls the number of rounds the firm is in the market by itself before the other firm enters and so in these rounds agents arrive and must choose firm 2. Importantly, we treat $X$ as an exogenous parameter (and not something optimally chosen by the entrant) and study the consequences of a fixed value of $X$. Thus, firm 2 is a monopolist for $X$ periods and, after $X$ rounds, firm 1 enters the market and each agent that enters in subsequent periods must select between the two firms. We want to understand what algorithms the incumbent (and the entrant) are incentivized to play. In particular, we are interested if introducing this asymmetry in entry induces firms who were previously incentivized to play $DG$ to play $TS$. As a result, we present the results of this experiment for $k = 20$ and on the Heavy Tail prior, where we saw that $DG$ was preferred to $TS$.

@@

Table \ref{ht_incum} shows the results of the simulations. We observe that, for the incumbent, $TS$ is a dominant strategy. In the appendix we include additional simulations where $X = 50$ and observe that $TS$ is not always a dominant strategy in this case. Qualitatively, these results are robust across the different priors we considered as well as across agent response models. Namely, for sufficiently large $X$, $TS$ is a dominant strategy for the incumbent.

Why do we observe this reversal? The intuition for this is that competition forces the firms to worry about their reputation which dissuades them from committing to algorithms that involve pure exploration in the early rounds. This intuition is very similar to that observed in the previous section by increasing warm start. In some sense one can view allowing one firm to temporarily be a monopolist as temporarily relaxing the ``incentive" component of exploration, exploitation, and incentives so that the incumbent firm only faces the classic tradeoff between exploration and exploitation. The incumbent only needs to worry about her reputation after $X$ periods when the entrant comes into the market and again needs to worry about incentivizing agents to select them over their competition. As a result, the incumbent is incentivized to commit to an algorithm that does exploration in the early rounds since she no longer suffers the same relative reputational cost that she would suffer under competition as long as the $X$ is sufficiently large that she can begin to recover the reputational costs of exploration. Thus, counterintuitively, by allowing one firm to be a monopoly and dominate the market, we can incentivize them to play $TS$ and thus get higher social welfare than under competition. [add some more economic intuition here]

[Include some discussion about the entrant]
